A Survey of Near-Term Exoskeleton Technology\\ (Draft 2.1)

### 2015-09-24 technology.tex
more updates
cga updates
cga-fixes

@@

\begin{verbatim}
07139975, 07131568
2015 IEEE International Conference on Robotics and Automation (ICRA)
Towards Balance Recovery Control for Lower Body Exoskeleton Robots
with Variable Stiffness Actuators: Spring-Loaded Flywheel Model
Corinne Doppmann, Barkan Ugurlu, Masashi Hamaya, Tatsuya Teramae,
Tomoyuki Noda, and Jun Morimoto
\end{verbatim}

@@

>>>>

A future white paper could discuss the addition of extra limbs to an
exoskeleton~\cite{IEEE07139896}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{design-goals.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{verbatim}
07139975, 07131568, 07251430.pdf
2015 IEEE International Conference on Robotics and Automation (ICRA)
Towards Balance Recovery Control for Lower Body Exoskeleton Robots
with Variable Stiffness Actuators: Spring-Loaded Flywheel Model
Corinne Doppmann, Barkan Ugurlu, Masashi Hamaya, Tatsuya Teramae,
Tomoyuki Noda, and Jun Morimoto
\end{verbatim}

@@

\section{Address what is the complexity penalty, weight penalty, 
and ``drag'' of actuator on individual joint motion.}
